--- 
title: "PCC Experiment"
author: "Marcelo Rosales"
date: "Created on 2021-05-05, updated:`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "Photo-Convertible Cell experiment notes and codes."
---

# Prerequisites

This is the _Photo convertible cell experiment notebook_ written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

To compile to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

Packages used in this project:  

```{r}

library(bookdown)
library(knitr)
library(rmarkdown)
```

Things I can`t find solutions to:
1. Shortcut key to auto-completion in R. Seems like it is option + Space, but it is system key for language change. A good tip [here](https://www.r-bloggers.com/2020/05/rstudio-shortcuts-and-tips/). 
1. Cant find the svn file in MBP20 Rstudio for git/svn configuration.
